CODE CHECK

### 2020-05-29 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- need to get wording straight: process/implementation/workflow (DN: suggest to use "workflow" for research-analysis workflow)
- https://codecheck.org.uk/process/
- _dimensions_ along which a check can vary
- independent/pre-submission (Peer_Coding) by author + colleagues
- AGILE
- premier (OA) publisher
- community OA / scholarly society with public peer review
- invited reproducibility paper track, cf. https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors
- on giving credit: public databases
  - https://www.reviewercredits.com/
  - Publons
  - ORCID
- compare with existing processes that are publicly documented
  - AJPS Verification Policy: https://ajps.org/ajps-verification-policy/
  - ...
- flexible level of detail? a check can be enhanced to (potentially semi-automatically) check for good practices
  - "A group of us in the @force11rescomm Software Citation Implementation Working Group produced a "Software Citation Checklist for Authors" https://t.co/4Noe66FsoX providing guidelines on how to cite software and describing why it is important and what software should be cited" via https://twitter.com/alegonbel/status/1207664922932453376?s=09)

@@

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- how can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion

@@

..

>>>>

- need to get wording straight: process/implementation/workflow (DN: suggest to use "workflow" for research-analysis workflow)
- https://codecheck.org.uk/process/
- _dimensions_ along which a check can vary
- independent/pre-submission (Peer_Coding) by author + colleagues
- AGILE
- premier (OA) publisher
- community OA / scholarly society with public peer review
- invited reproducibility paper track, cf. https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors
- on giving credit: public databases
  - https://www.reviewercredits.com/
  - Publons
  - ORCID
- compare with existing processes that are publicly documented
  - AJPS Verification Policy: https://ajps.org/ajps-verification-policy/
  - ...
- flexible level of detail? a check can be enhanced to (potentially semi-automatically) check for good practices
  - "A group of us in the @force11rescomm Software Citation Implementation Working Group produced a "Software Citation Checklist for Authors" https://t.co/4Noe66FsoX providing guidelines on how to cite software and describing why it is important and what software should be cited" via https://twitter.com/alegonbel/status/1207664922932453376?s=09)
- focus on ECR as codecheckers
  - ECR are the one's breaking new ground in schol comm, cf. the percentages of career stages submitting registered reports on slide 20 > https://osf.io/2vjus/

@@

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- how can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
- can we establish code checks as a type of review within the schol comm metadata (or should we?) > we should not, put them on the same level as reviews!

@@

SE ...; DN ...; see [CRediT](https://casrai.org/credit/).
